Nathan Greenslit Data Analysis Project

### 2023-03-14 code/analysis_code/dust/dust_and_copies.qmd
Cleaned up code

---
title: "Dust_Copies_Plot"
format:
  html:
    theme: default
---

Library
```{r}
library(here)
library(tidyverse)
library(ggpubr)
```

Load Data that has just DUST CONC
```{r}
#Summed Dust Concentration per day
dust_sum<-readRDS(file = here("data", "processed_data", "dust_copies", "dust_copies_sum.rds")) 
copies<- read_csv(here("data", "processed_data", "total_clean_copies.csv")) 
```

Daily Data frame with Summed dust by day
```{r}
daily_dust_sum<- dust_sum %>%
  filter(between(date, as.Date('2022-07-07'), as.Date('2022-07-19'))) #We do not have copies_mL for 2022-07-10. No sampling occured then.

@@

Plot Daily Dust Concentration
```{r}
dust_fig<- daily_dust_sum %>% ggplot() +geom_line(
  aes(x = date,
      y = dust),
  color = "#935d2e",
  size = 1)+
  theme_bw()+
  labs(
    x = "Date",
    y = "Dust Aerosol Optical Density")+
  theme(
    axis.title.y = element_text(size = 15),
    axis.text.y = element_text(size = 10),
    axis.title.x = element_text(size = 15),
    axis.text.x = element_text(size = 10))

>>>>

---
title: "Dust_Copies_Plot"
format:
  html:
    theme: default
---
**This script is good for visualizing copies per mL data and dust data.**
Library
```{r}
library(here)
library(tidyverse)
library(ggpubr)
```

Load Data 
```{r}
dust_sum<-read_csv(here("data", "processed_data", "dust_master.csv")) 
copies<- read_csv(here("data", "processed_data", "total_clean_copies.csv")) 
```

Daily Data frames
```{r}
daily_dust_sum<- dust_sum %>%
  filter(between(date, as.Date('2022-07-07'), as.Date('2022-07-19')))

@@

Plot Daily Dust Concentration
```{r}
dust_fig<- daily_dust_sum %>% ggplot() +geom_line(
  aes(x = date,
      y = t7sum),
  color = "#935d2e",
  size = 1)+
  theme_bw()+
  labs(
    x = "Date",
    y = "Dust Aerosol Optical Density")+
  theme(
    axis.title.y = element_text(size = 15),
    axis.text.y = element_text(size = 10),
    axis.title.x = element_text(size = 15),
    axis.text.x = element_text(size = 10))

### 2023-03-14 code/analysis_code/env/env_par.qmd
Cleaned up code

---
title: "Environmental Parameters"
format:
  html:
    theme: default
---
*This data set contains environmental parameters: Temp and Salinity. I am waiting on an updated Nutrient data set*

Libraries
```{r}
library(tidyverse)
library(here)
library(ggpubr)
```

Load Data
```{r}
d1<- read_csv(here("data", "raw_data", "ysi_.csv"))
```

Daily data frame
```{r}
d1<- d1 %>%
  mutate(site = recode(site, "BO" = "Blind Oso",
                             "C2" = "Canals",
                            "RD" = "Gulf"))
daily<- d1 %>%
  filter(type %in% "Daily")

@@

Plotting Daily Salinity
```{r}
sal<- daily %>% ggplot() + geom_line(
  aes(
    x = date,
    y = salinity,
    color = site),
  size = 1)+
  theme_bw()+
  labs(
    x = "Date",
    y = "Salinity",
    title = "Salinity across Daily Time Series by Site",
    color = "Site")+
  theme(
    plot.title= element_text(hjust = 0.5, size = 20),
    axis.title.x = element_text(size = 15),
    axis.title.y = element_text(size = 15),
    axis.text.x = element_text(size = 10),
    axis.text.y = element_text(size = 10),
    legend.position = "none")+
    scale_color_manual(values = c("Blind Oso" = "#809C52",
                                "Canals" = "#ba4716",
                                "Gulf" = "4c848c"))

>>>>

---
title: "Environmental Parameters"
format:
  html:
    theme: default
---
*This data set contains environmental parameters: Temp and Salinity, among other environmental parameters.*

Libraries
```{r}
library(tidyverse)
library(here)
library(ggpubr)
library(lubridate)
```

Load Data
```{r}
d1<- read_csv(here("data", "processed_data", "tx_master.csv"))
```

Daily data frame
```{r}
daily<- d1 %>%
  filter(date %in% c(as.Date("2022-07-07"):as.Date("2022-07-19"))) %>%
  select(!...1)
```

@@

Plotting Daily Salinity
```{r}
sal<- daily %>% ggplot() + geom_line(
  aes(
    x = date,
    y = sal,
    color = site),
  size = 1)+
  theme_bw()+
  labs(
    x = "Date",
    y = "Salinity",
    title = "Salinity across Daily Time Series by Site",
    color = "Site")+
  theme(
    plot.title= element_text(hjust = 0.5, size = 20),
    axis.title.x = element_text(size = 15),
    axis.title.y = element_text(size = 15),
    axis.text.x = element_text(size = 10),
    axis.text.y = element_text(size = 10),
    legend.position = "none")+
    scale_color_manual(values = c("Blind Oso" = "#809C52",
                                "Canals" = "#ba4716",
                                "Gulf" = "4c848c"))

### 2023-03-14 data/raw_data/rawdata_README.Rmd
Cleaned up code

This folder contains dust concentrations in AOT from the Naval Reserach lab, environmental parameters (temperature and salinity) that were collected during the summer at the three sites, and  qPCR results for Total Vibrio.

>>>>

This folder contains three raw data sets:\
(1) `dust.csv`:dust concentrations in AOT from the Naval Research lab. Concentrations (AOT) were collected at 4 time points (UTC): T0,T6,T12, and T18.\
(2) `copies_master.csv`:  qPCR results for Total Vibrio enumeration.

### 2023-03-14 products/manuscript/Manuscript.qmd
Cleaned up code

## Data aquisition

@@

Variables will include `Temperature (°C)`, `Salinity`, `Nitrate`, `Phosphate`, `Copies/mL` produced using quantitative PCR. Provides gene copies of Vibrio bacteria (I am hoping to also get data about specific species), and `Dust Concentration (AOT)` from the naval research laboratory satellite data.

@@

This project works with three primary data sets. (1) Enumeration of Vibrio bacteria as copies/mL from quantitative PCR (copies_master.csv), (2) Dust concentrations as aerosol optical thickness (AOT) derived from the Naval Research Lab (nrl_conc.csv), and (3) Temperature and Salinity across the daily time series (ysi\_.csv). Below is a brief summary of how each data set was cleaned. More details can be found in the supplementary files, containing the code and comments describing what each line does. Please refer to the `project_README.md` file located in the NathanGreenslit-MADA-Project folder for details on the repository contents and  instructions on reproducibility

@@

Quantitative PCR provides enumeration results as "cycle threshold or Cq" values. This depicts the cycle number in which enough of the DNA target was detectable to be amplified. Lower Cq values correspond to higher target concentrations (as it takes less cycles to amplify), and vice verse for higher Cq values. The cleaning of this data set consisted of converting these Cq values into something that can be used to quantify Vibrio (copies of target per mL of seawater). To do so, I needed to take into account the amount of water sample that was concentrated on a filter, the total amount of DNA that was eluted following a DNA extraction, and the amount of DNA template added to each mix for qPCR (to name a few). Taking these into account, we are able to calculate our way from Cq values to copies of Vibrio per mL of seawater. qPCR was conducted in triplicate, so the last step was to take the average of the three replicates to have a final value per sample. A date column was also added for each sample.

@@

![](images/dust_sum_daily.png)

This figure depicts the summed dust concentration (time points 0hr-18hr) across the daily time series. During the time series, two small period of higher dust AOT occurred on the 9th and 13th respectively. A much larger spike in AOT was observed on the 16th.

@@

![](images/vib_dust_daily.png)

The top portion of the figure depicts total enumerated Vibrio as copies per mL, with color by site. There is a noticeable shift in copies in the Gulf site, a less noticeable but still present shift in Blind Oso Bay, and practically no changes in the Canal site. The bottom portion of the figure depicts the dust concentration (AOT) across the daily time series. Initial shift in copies per mL at the Guld and Blind Oso occur around initial dust introduction on the 13th, and experience another shift around the time of higher dust input on the 16th.

>>>>

## Data acquisition

@@

Variables will include `Temperature (°C)`, `Salinity`, `Nitrate`, `Phosphate`, `Copies/mL` produced using quantitative PCR, and `Dust Concentration (AOT)` from the naval research laboratory satellite data.

@@

This project works with three primary data sets. (1) Enumeration of Vibrio bacteria as copies/mL from quantitative PCR (copies_master.csv), (2) Dust concentrations as aerosol optical thickness (AOT) derived from the Naval Research Lab (nrl_conc.csv), and (3) Temperature and Salinity across the daily time series (ysi_2.csv). Below is a brief summary of how each data set was cleaned. More details can be found in the supplementary files, containing the code and comments describing what each line does. Please refer to the `project_README.md` file located in the NathanGreenslit-MADA-Project folder for details on the repository contents and instructions on reproducibility

@@

Quantitative PCR provides enumeration results as "cycle threshold or Cq" values. This depicts the cycle number in which enough of the DNA target was present to be amplified and thus detected. Lower Cq values correspond to higher target concentrations (as it takes less cycles to amplify), and vice verse for higher Cq values. The cleaning of this data set consisted of converting these Cq values into something that can be used to quantify Vibrio (copies of target per mL of seawater). To do so, I needed to take into account the amount of water sample that was concentrated on a filter, the total amount of DNA that was eluted following a DNA extraction, and the amount of DNA template added to each mix for qPCR (to name a few). Taking these into account, we are able to calculate our way from Cq values to copies of Vibrio per mL of seawater. qPCR was conducted in triplicate, so the last step was to take the average of the three replicates to have a final value per sample. A date column was also added for each sample.

@@

![](images/paste-0FE55FAA.png)

This figure depicts the summed dust concentration 24hr prior to sample collection (time points 13hr--> 7hr the next day) across the daily time series. During the time series, two small periods of higher dust AOT occurred on the 9th and 13th respectively. A much larger spike in AOT was observed on the 16th.

@@

![](images/paste-C33B6E43.png)

The top portion of the figure depicts total enumerated Vibrio as copies per mL, with color by site. There is a noticeable shift in copies in the Gulf site, a less noticeable but still present shift in Blind Oso Bay, and practically no changes in the Canal site. The bottom portion of the figure depicts the dust concentration (AOT) across the daily time series. Initial shift in copies per mL at the Gulf and Blind Oso occur 24-48hr following initial dust introduction on the 13th, and experience another shift around 24-48hr of higher dust input on the 16th.
